Stack Safety as a Security Property

### 2021-03-02 main.tex
Reorganized structure, fixed powerset
Edits to section 4

@@

The step function of the machine takes a machine state and produces a
pair of a machine state and an {\em observation}, which may be either
silent (written \(\tau\)) or a word of data\ifaftersubmission\bcp{This is a rather concrete
  choice!  Why not leave the set of observations abstract?}\fi that the machine
communicates to the outside world:
%
\[\obs \in \OBSS = \{\tau\} \uplus \WORDS\]
\[\mach \stepstoobs[\obs] \mach' \in \MACHS \rightarrow \MACHS \times \OBSS \]
%
This step function is total, so the machine's execution traces
(defined in \cref{sec:traces}) are infinite.

@@

\judgmenttwo{\(\mpstate{\mach}{\pol} \stepstopol{\obs} \mpstate{\mach'}{\pol'}\)}
            {\(\mach, \context \constep \context'\)}
            {\(\mpcstate{\mach}{\pol}{\context} \stepstocon{\obs}
               \mpcstate{\mach'}{\pol'}{\context'}\)}

@@

The ``trace-of'' operator, written \(\mpcstatename \hookrightarrow \MPCT\),
coinductively relates an initial state with the trace of states
produced by repeated application of step, and potentially cut short by
the policy component.

\judgment{\(\neg \exists \pol' . \mpcstate{\mach}{\pol} \polstep \pol'\)}
         {\(\mathit{obsforward} ~ \mpcstate{\mach}{\pol}{\context} ~ \obs =
           \mpcstate{\mach}{\pol}{\context},\obs\)}
%
\judgmenttwo{\(\mpcstate{\mach}{\pol}{\context} \stepstoobs[\obs'] \mpcstate{\mach'}{\pol'}{\context'}\)}
            {\(\mathit{obsforward} ~ \mpcstate{\mach'}{\pol'}{\context'} ~ \obs' = \machT\)}
            {\(\mathit{obsforward} ~ \mpcstate{\mach}{\pol}{\context} ~ \obs =
              (\mpcstate{\mach}{\pol}{\context},\obs) \machT\)}%
%
\judgment{\(\mathit{obsforward} ~ \mpcstatename ~ \tau = \machT\)}
         {\(\mpcstatename \hookrightarrow \machT\)}

@@

\judgmentthree{\(\pi_\mach ~ \mpcstatename \stepstoobs[\obs'] \pi_\mach ~ \mpcstatename'\)}
              {\(\mpcstatename' \hookrightarrow \MPCT\)}
              {\(\mathit{obsforward} ~ \obs' ~ \MPCT = \obsT\)}
              {\(\mathit{obsforward} ~ \obs ~ \mpcstatename \MPCT = \obs\obsT\)}%
\judgment{}
         {\(\mathit{obsforward} ~ \obs ~ \mpcstatename = \obs\)}

@@

\judgment{\(\mathit{obsforward} ~ \tau ~ \MPCT = \obsT\)}
         {\(\pi_\obs ~ \MPCT = \obsT\)}
\noindent
(We use juxtaposition of an element and a sequence to represent ``cons.'')

@@

\[\ann \in \ANNS ::= \mathscr{P}(\{\callmap, \retmap\})\]
\[\codemap \in \CODEMAPS ::= \WORDS \rightharpoonup \FUNIDS \times \option{\ann}\]

@@

\subsection{Stack Safety with Sharing}
\[\ann \in \ANNS ::= \mathscr{P}(\{\callmap, \retmap\} \cup
\{\sharemap ~ P | P \subseteq \MACHS \times \COMPONENTS \} \cup
\{\passmap ~ P | P \subseteq \MACHS \times \COMPONENTS \})\]

@@

\section{Coroutine Safety}
\[\ann \in \ANNS ::= \mathscr{P}(\{\callmap, \retmap, \yieldmap\} \cup
\{\sharemap ~ P | P \subseteq \MACHS \times \COMPONENTS \} \cup
\{\passmap ~ P | P \subseteq \MACHS \times \COMPONENTS \})\]

@@

Recall that our properties use a compiler-derived code-map determine
which addresses are instructions and which functions they belong to, as well
as annotating them as calls, returns, and yields, as well as sharing information.
We now extend it with an annotation for valid entry points:
\[\ann \in \ANNS ::= \mathscr{P}(\{\callmap, \retmap, \yieldmap, \entmap\} \cup
\{\sharemap ~ P | P \subseteq \MACHS \times \COMPONENTS \} \cup
\{\passmap ~ P | P \subseteq \MACHS \times \COMPONENTS \})\]

@@

@@

>>>>

\newcommand{\powerset}{\raisebox{.15\baselineskip}{\Large\ensuremath{\wp}}}

@@

The step function of the machine takes a machine state and produces a
pair of a machine state and an {\em observation}, which may be either
silent (written \(\tau\)) or a word of data that the machine
communicates to the outside world:
\ifaftersubmission\bcp{This is a rather concrete
  choice!  Why not leave the set of observations abstract?}\fi
%
\[\obs \in \OBSS = \{\tau\} \uplus \WORDS\]
\[\mach \stepstoobs[\obs] \mach' \in \MACHS \rightarrow \MACHS \times \OBSS \]
%
This step function is total, so the machine's execution traces
(defined in \cref{sec:traces}) are infinite.

@@

\judgmenttwo{\(\mpstate{\mach}{\pol} \stepstopol[\obs] \mpstate{\mach'}{\pol'}\)}
            {\(\mach, \context \constep \context'\)}
            {\(\mpcstate{\mach}{\pol}{\context} \stepstocon[\obs]
               \mpcstate{\mach'}{\pol'}{\context'}\)}

@@

The ``trace-of'' operator, written \(\mpcstatename \hookrightarrow \MPCT\),
coinductively relates an initial state with the trace of states
produced by repeated application of step, and potentially cut short by
the policy component. The {\sc Default} rule applies only if the other does not.
(We use juxtaposition of an element and a trace to represent ``cons.'')

\begin{minipage}{.4\textwidth}
\judgmenttwo{\(\mpcstatename \stepstocon \mpcstatename'\)}
            {\(\mpcstatename' \hookrightarrow \MPCT\)}
            {\(\mpcstatename \hookrightarrow \mpcstatename' \MPCT\)}%
\end{minipage}
\begin{minipage}{.4\textwidth}
\judgment[Default]
         {}
         {\(\mpcstatename \hookrightarrow \mpcstatename\)}
\end{minipage}
%

@@

\judgmentthree{\(\mpcstatename \stepstocon[\obs'] \mpcstatename'\)}
              {\(\mpcstatename' \hookrightarrow \MPCT\)}
              {\(\mathit{obsforward} ~ \obs' ~ \MPCT = \obsT\)}
              {\(\mathit{obsforward} ~ \obs ~ \mpcstatename \MPCT = \obs\obsT\)}%
\judgment{}
         {\(\mathit{obsforward} ~ \obs ~ \mpcstatename = \obs\)}

@@

\judgment{\(\mathit{obsforward} ~ \tau ~ \MPCT = \obsT\)}
         {\(\pi_\obs(\MPCT) = \obsT\)}
\noindent

@@

\[\ann \in \ANNS ::= \powerset(\{\callmap, \retmap\})\]
\[\codemap \in \CODEMAPS ::= \WORDS \rightharpoonup \FUNIDS \times \option{\ann}\]

@@

\subsection{Stack Safety with Sharing}
\[\ann \in \ANNS ::= \powerset(\{\callmap, \retmap\} \cup
\{\sharemap ~ P | P \subseteq \MACHS \times \COMPONENTS \} \cup
\{\passmap ~ P | P \subseteq \MACHS \times \COMPONENTS \})\]

@@

\section{Coroutine Safety}
\[\ann \in \ANNS ::= \powerset(\{\callmap, \retmap, \yieldmap\} \cup
\{\sharemap ~ P | P \subseteq \MACHS \times \COMPONENTS \} \cup
\{\passmap ~ P | P \subseteq \MACHS \times \COMPONENTS \})\]

@@

Recall that our properties use a compiler-derived code-map determine
which addresses are instructions and which functions they belong to, as well
as annotating them as calls, returns, and yields, as well as sharing information.
We now extend it with an annotation for valid entry points:
\[\ann \in \ANNS ::= \powerset(\{\callmap, \retmap, \yieldmap, \entmap\} \cup
\{\sharemap ~ P | P \subseteq \MACHS \times \COMPONENTS \} \cup
\{\passmap ~ P | P \subseteq \MACHS \times \COMPONENTS \})\]

@@

\section{Programming Logic Perspective}

@@

\section{Randomized Testing}
